%------------------------
% Resume - GenAI / Platform Focused
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{{\LARGE Vaibhav Goswami}} & Email: \href{mailto:vabg96@yahoo.com}{vabg96@yahoo.com} \\
\href{https://bluekap.github.io}{Portfolio: bluekap.github.io} & Mobile: +48 795-345-494 \\
Github: github.com/bluekap & Location: Gdańsk, Poland \\
\end{tabular*}

%-----------SKILLS-----------------
\section{Skills Summary}
\resumeSubHeadingListStart
\resumeSubItem{Languages}{Python, SQL}
\resumeSubItem{ML \& AI}{TensorFlow, Keras, Scikit-learn, LangChain, OpenCV, LLMs, RAG, Embeddings, Semantic Search, Prompt Engineering}
\resumeSubItem{Cloud \& MLOps}{AWS (SageMaker, Bedrock, Lambda), GCP (BigQuery, Dataflow), Docker, Kubernetes, Terraform}
\resumeSubItem{Data Platforms}{DynamoDB, BigQuery, Snowflake, Pub/Sub}
\resumeSubItem{Tools}{Git, CI/CD, Flask, FastAPI}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

%---- Thomson Reuters ----
\resumeSubheading
  {Thomson Reuters}{Gdańsk, Poland}
  {Senior Software Engineer}{June 2022 -- Present}
\resumeItemListStart
  \resumeItem{Enterprise Generative AI Platform}
  {Core contributor and technical lead for an enterprise-scale Generative AI platform serving \textbf{20k+ monthly users}. Took the platform from early design to production adoption across multiple internal teams.}

  \resumeItemWithoutTitle
  {Designed a scalable, serverless architecture enabling rapid onboarding of applied AI use cases, focusing on improving the quality and relevance of search results through document analysis, summarization, and workflow automation.}

  \resumeItem{LLM Integration \& Orchestration}
  {Integrated and standardized access to multiple LLM providers including OpenAI, Anthropic (Claude), Google Gemini, and open-source Llama models. Built abstraction layers for prompt management, model selection, and evaluation.}

  \resumeItem{RAG, Embeddings \& Semantic Search}
  {Enabled creation of robust Retrieval-Augmented Generation (RAG) pipelines utilizing embeddings-based retrieval and semantic search. Expanded retrieval capabilities to seamlessly query third-party data sources using LangChain, tool/function calling, and Model Context Protocol (MCP) concepts for structured context exchange.}

  \resumeItem{Platform Data \& Search Infrastructure}
  {Designed and optimized scalable data infrastructure for high-throughput GenAI workloads. Reduced latency and cost of the retrieval system while managing execution metadata, prompt versions, and agent state.}

  \resumeItem{ML Model Monitoring}
  {Previously led development of Model Performance and Data Drift Monitoring services within the Enterprise AI Platform, supporting \textbf{500+ users} and production ML systems.}
\resumeItemListEnd
\vspace{5pt}

%---- HSBC ----
\resumeSubheading
  {HSBC Bank PLC}{Hyderabad, India}
  {Senior Software Engineer}{July 2019 -- April 2022}
\resumeItemListStart
  \resumeItem{Machine Learning Platform Engineering}
  {Built an automated ML pipeline on Kubernetes to standardize model training and deployment, reducing manual effort by \textbf{90\%} and improving reproducibility across teams.}

  \resumeItem{Cloud \& DevOps}
  {Led GCP migration initiatives and implemented Terraform-based infrastructure pipelines, reducing deployment errors by \textbf{95\%} and saving \textbf{\$5k annually} through infrastructure optimization.}
\resumeItemListEnd
\vspace{5pt}

%---- UST Global ----
\resumeSubheading
  {UST Global}{Chennai, India}
  {Machine Learning Intern}{July 2018 -- December 2018}
\resumeItemListStart
  \resumeItem{Computer Vision Project}
  {Developed a car damage detection and repair cost estimation system using Mask-RCNN, achieving \textbf{91\% accuracy} on a dataset of 10,000+ images.}

  \resumeItemWithoutTitle
  {Applied transfer learning and image augmentation techniques; project was showcased at the D3+ Industry Expo to business stakeholders.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------------
\vspace{-5pt}
\section{Publications \& Technical Writing}
\resumeSubHeadingListStart
\resumeSubItem{AWS Machine Learning Blog (Co-author)}
{\href{https://aws.amazon.com/blogs/machine-learning/democratizing-ai-how-thomson-reuters-open-arena-supports-no-code-ai-for-every-professional-with-amazon-bedrock/}
{``Democratizing AI: How Thomson Reuters Open Arena supports no-code AI with Amazon Bedrock''} — November 2025.}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\vspace{-5pt}
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
  {Birla Institute of Technology and Science (BITS Pilani)}{Goa Campus}
  {B.E. (Hons.) Electronics \& Instrumentation}{July 2015 -- August 2019}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{CodeGraph - Interactive Repository Visualizer}{
Built a full-stack web application that transforms GitHub repositories into interactive dependency graphs with real-time metrics and physics-based visualizations. Architected a FastAPI backend that clones repositories, parses Python imports using AST, and calculates complexity metrics with Radon and NetworkX. (January 2026)}
\resumeSubItem{Automatic Sudoku Solver from Image}
{An AI-powered web application that solves Sudoku puzzles from camera images in seconds. It uses computer vision to detect the grid and deep learning OCR to recognize digits. }
\vspace{2pt}


%-----------CERTIFICATIONS-----------------
\vspace{-5pt}
\section{Professional Certifications}
\resumeSubHeadingListStart
\resumeSubItem{AWS}{Developer Associate (2022)}
\resumeSubItem{Google Cloud Platform}{Professional Data Engineer (2021)}
\resumeSubItem{TensorFlow}{TensorFlow Developer Certificate (2021)}
\resumeSubItem{Google Cloud Platform}{Associate Cloud Engineer (2020)}
\resumeSubHeadingListEnd
\resumeSubHeadingListEnd
\end{document}
